Lynott et al. (2014) - Potential error in statistics reporting

### 2017-11-17 Leftovers/NHST_and_TOST.Rmd
update folder structure

---
title: "Simulating NHST and TOST"
output:
  html_document: default
  html_notebook: default
  pdf_document: default
editor_options: 
  chunk_output_type: console
---

>>>>

---
title: "Simulating NHST and TOST"
output:
  pdf_document: default
  html_notebook: default
  html_document: default
editor_options: 
  chunk_output_type: console
---

### 2017-11-17 manuscript.Rmd
update folder structure

lang              : "english"
class             : "man"
output            : papaja::apa6_pdf
---

```{r include = FALSE}
library("papaja")

@@

# Plot H0 and H1 regions for different significance tests
source("H0H1_plot.R")
```

>>>>

lang              : "english"
class             : "man"
output            : papaja::apa6_pdf
---
getwd()
```{r include = FALSE}
library("papaja")

@@

# Plot H0 and H1 regions for different significance tests
source("H0H1_plot.R")
getwd()
```
